Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-04-03 paper/manuscript.Rmd
del Fish ref

Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration [@Leblond2016],
to avoid predators [@Bergerud1985], and access islands during calving
[@Bergerud1990]. Even for adept swimmers like caribou, the energetic expenditure
of swimming for quadrupedal mammals is significantly higher than walking or
running, <!--[@Fish1993]--> and drowning is also possible [@Miller1985]. Despite
the abundance of coastal and island caribou herds, only a handful of examples
have documented caribou swimming in the ocean [e.g. @Miller1995; @Miller2002;
@Jeffery2007; @Ricca2012].

>>>>

Caribou (*Rangifer tarandus*) are exceptional swimmers. Ample evidence exists
that caribou swim in streams, rivers, and lakes during migration [@Leblond2016],
to avoid predators [@Bergerud1985], and access islands during calving
[@Bergerud1990]. Even for adept swimmers like caribou, the energetic expenditure
of swimming for quadrupedal mammals is significantly higher than walking or
running, and drowning is also possible [@Miller1985]. Despite
the abundance of coastal and island caribou herds, only a handful of examples
have documented caribou swimming in the ocean [e.g. @Miller1995; @Miller2002;
@Jeffery2007; @Ricca2012].
